# Reproducible Research: Peer Assessment 1


## Loading and preprocessing the data



```{r}
setwd("/Users/minh-duy/Documents/MyWork/Learning/DataScienceSpecialization/5.ReproducibleResearch/working/RepData_PeerAssessment1")

if (!file.exists("activity.csv")) {
    unzip("activity.zip")
}

data <- read.csv("activity.csv")
data$date <- as.Date(data$date) 
```

## What is mean total number of steps taken per day?

1. Calculate the total number of steps per day, ignoring missing values for now.
```{r}
stepspday <- tapply(data$steps, data$date, mean)
```

2. Make a histogram of the total number of steps taken each day
```{r fig.width=7, fig.height=6}
hist(stepspday, main = "Histogram of the total number of steps taken each day", xlab= "Steps per day")
```

3. Calculate and report the mean and median total number of steps taken per day
```{r}
mean(stepspday, na.rm = TRUE)
median(stepspday, na.rm = TRUE)
```

## What is the average daily activity pattern?



## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
